### 2023-08-16 introduction.tex
up

{\bf Resiliences.}  
%		We now give the definition of two kinds of resilience: the (general) resilience and the state-resilience. 
The (general) resilience property for a transition system $\mathscr{S} = (S,\rightarrow )$ and two subsets of states $\Bad,\Safe \subseteq S$ can be stated as an home-space problem : $\mathscr{S}$ is ($\Bad,\Safe$)-resilient if $\post^*(\Bad) \subseteq \pred^*(\Safe)$; 
\mathieu{Pas la définition exacte,  $\Bad \subseteq \pred^*(\Safe)$ n'est pas la même chose que $\post^*(\Bad) \subseteq \pred^*(\Safe)$ sauf cas particulier comme typiquement Bad et Safe complémentaire. Changer la formulation.}
similarly, $\mathscr{S}$ is (\Bad,\Safe)-state-resilient for an initial state $s_0$ if $\post^*(s_0) \cap \Bad \subseteq \pred^*(\Safe)$.
We will study three decidability questions for each of type of resilience.
The resilience problem is to decide whether a transition system $\mathscr{S} = (S,\rightarrow )$ is ($\Bad,\Safe$)-resilient (for two given subsets of states $\Bad,\Safe \subseteq S$).
The $k$-resilience problem is to decide whether $\post^*(\Bad) \subseteq \pred^{\leq k}(\Safe)$ (for a given $k$) and 
the bounded resilience problem is to decide whether there exists an $k$ such that $\mathscr{S}$ is ($\Bad,\Safe$)-$k$-resilient. We adapt these three definitions to state-resilience.

@@

\item Surprinsingly, the general undecidability statements about resilience were not known neither proved. We show that resilience and {\sc State-resilience} problems are both undecidable for WSTS with strong compatibility. 
\alain{harminiser les notations des pbs {\sc State-resilience} ou  State-resilience ?}
\mathieu{je pense dans l'intro on peut conserver State-resilience et par contre une fois le probleme de {\sc State-resilience} proprement défini c'est cette notation qu'il faudrait utiliser}
%Moreover, state-resilience,
%bounded-state-resilience and
% $k$-state-resilience
%are undecidable for WSTS with strong compatibility having an effective pred-basis. 
Moreover, {\sc State-resilience},
{\sc Bounded-state-resilience} and
{\sc $k$-state-resilience}
are undecidable for strongly upward-compatible WSTS with effective pred-basis
when
$\Safe=\uparrow \Safe$. We made a reduction of zero-reachability in reset-VASS to {\sc State-resilience} in reset-VASS.

@@

\item We generalize the main theorem of \cite{DBLP:journals/corr/abs-2108-00889,DBLP:conf/gg/Ozkan22} by relaxing the strong compatibility hypothesis.
%: {\sc State-resilience} is still decidable for 
% WSTS with effective 
%$\uparrow$ $\post^*$ basis
%when
%$\Safe=\uparrow \Safe$
%and $\Bad=\downarrow \Bad$. 
We also show that removing the effective 
$\uparrow$ $\post^*$ basis hypothesis leads to undecidability. We extend and prove the main result in  \cite{DBLP:journals/corr/PrasadZ16} : the three state-resilience problems are decidable for ideal-effective WSTS with downward and upward compatibilities ({\sc $k$-state-resilience} and {\sc bounded-state-resilience} are decidable for ideal-effective WSTS with strong downward compatibility).
%

>>>>

{\bf Resiliences.}  
%		We now give the definition of two kinds of resilience: the (general) resilience and the state-resilience. 
The (general) resilience property for a transition system $\mathscr{S} = (S,\rightarrow )$ and two subsets of states $\Bad,\Safe \subseteq S$ consists of the following: $\mathscr{S}$ is ($\Bad,\Safe$)-resilient if
$\Bad \subseteq \pred^*(\Safe)$. In the case 
it 
can be stated as an home-space problem : $\mathscr{S}$ is ($\Bad,\Safe$)-resilient if $\post^*(\Bad) \subseteq \pred^*(\Safe)$.
Similarly, $\mathscr{S}$ is (\Bad,\Safe)-state-resilient for an initial state $s_0$ if  
$\post^*(s_0) \cap \Bad \subseteq \pred^*(\Safe)$.
We will study three decidability questions for each of type of resilience.
The resilience problem is to decide whether a transition system $\mathscr{S} = (S,\rightarrow )$ is ($\Bad,\Safe$)-resilient (for two given subsets of states $\Bad,\Safe \subseteq S$).
The $k$-resilience problem is to decide whether $\post^*(\Bad) \subseteq \pred^{\leq k}(\Safe)$ (for a given $k$) and 
the bounded resilience problem is to decide whether there exists an $k$ such that $\mathscr{S}$ is ($\Bad,\Safe$)-$k$-resilient. We adapt these three definitions to state-resilience.

@@

\item Surprinsingly, the general undecidability statements about resilience were not known neither proved. We show that resilience and { State-resilience} problems are both undecidable for WSTS with strong compatibility. 
% \alain{harminiser les notations des pbs { State-resilience} ou  State-resilience ?}
% \mathieu{je pense dans l'intro on peut conserver State-resilience et par contre une fois le probleme de {\ State-resilience} proprement défini c'est cette notation qu'il faudrait utiliser}
%Moreover, state-resilience,
%bounded-state-resilience and
% $k$-state-resilience
%are undecidable for WSTS with strong compatibility having an effective pred-basis. 
Moreover, { State-resilience},
{ Bounded-state-resilience} and
{ $k$-state-resilience}
are undecidable for strongly upward-compatible WSTS with effective pred-basis
when
$\Safe=\uparrow \Safe$. We made a reduction of zero-reachability in reset-VASS to {\ State-resilience} in reset-VASS.

@@

\item We generalize the main theorem of \cite{DBLP:journals/corr/abs-2108-00889,DBLP:conf/gg/Ozkan22} by relaxing the strong compatibility hypothesis.
%: {\ State-resilience} is still decidable for 
% WSTS with effective 
%$\uparrow$ $\post^*$ basis
%when
%$\Safe=\uparrow \Safe$
%and $\Bad=\downarrow \Bad$. 
We also show that removing the effective 
$\uparrow$ $\post^*$ basis hypothesis leads to undecidability. We extend and prove the main result in  \cite{DBLP:journals/corr/PrasadZ16} : the three state-resilience problems are decidable for ideal-effective WSTS with downward and upward compatibilities ({ $k$-state-resilience} and { bounded-state-resilience} are decidable for ideal-effective WSTS with strong downward compatibility).
%
